sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-11-24 doc/paper.Rmd

knitr::kable(d, format = "latex", caption = "Comparison of functionality between eight R packages that can fit geostatistical GLMMs.", 
  booktabs = TRUE, 
  linesep = c(
    rep('', 4), # coefs
    '\\addlinespace',
    rep('', 5), # correlation stuff
    '\\addlinespace',
    rep('', 11), # likelihood
    '\\addlinespace',
    rep('', 2), # bayes
    '\\addlinespace'
  ),
  escape = FALSE, row.names = FALSE) %>%
  kableExtra::kable_styling(font_size = 8) %>% 
  kableExtra::footnote(
    number = c(
      "SPDE approach as in Miller et al. (2019).",
      "Technically possible but non-trivial.",
      "Zero-inflated NB2 only.",
      "Tweedie power parameter fixed for \\\\texttt{mgcv::gamm()}.",
      "Technically possible but non-trivial.",
      "Technically possible but non-trivial."
    ),
    escape = FALSE
  )
```

>>>>

knitr::kable(d, format = "latex", caption = "Comparison of functionality between eight R packages that can fit geostatistical GLMMs.", 
  booktabs = TRUE, 
  linesep = c(
    rep('', 5), # coefs
    '\\addlinespace',
    rep('', 5), # correlation stuff
    '\\addlinespace',
    rep('', 11), # likelihood
    '\\addlinespace',
    rep('', 2), # bayes
    '\\addlinespace'
  ),
  escape = FALSE, row.names = FALSE) %>%
  kableExtra::kable_styling(font_size = 8) %>% 
  kableExtra::footnote(
    number = c(
      "SPDE approach as in Miller et al. (2019).",
      "Technically possible but non-trivial.",
      "Zero-inflated NB2 only.",
      "Tweedie power parameter fixed for \\\\texttt{mgcv::gamm()}.",
      "Technically possible but non-trivial.",
      "Technically possible but non-trivial."
    ),
    escape = FALSE
  )
```
